\begin{thebibliography}{99}
\addcontentsline{toc}{section}{Список литературы}

% INTRODUCTION =========================================================================

\bibitem{FAIR}
``FAIR Baseline Technical Report,'' GSI, Darmstadt (2006) 92~p. \\
\blueurl{www.fair-center.eu/fileadmin/fair/publications_FAIR/FAIR_BTR_1.pdf}

% --- CBM ------------------------------------------------------------------------------

\bibitem{CBMBook}
B.~Friman, C.~Hohne, J.~Knoll, S.~Leupold, J.~Randrup, R.~Rapp and P.~Senger, ``The CBM physics book: Compressed baryonic matter in laboratory experiments,''
Lect.\ Notes Phys.\ {\bf 814} (2011) pp. 980.

\bibitem{CBMSIS100}
P.~Senger and V.~Friese, ``The CBM Collaboration: Nuclear Matter Physics at SIS-100,'' GSI, Darmstadt (2012) 18~p.

\bibitem{CBM_TSR}
``Compressed Baryonic Matter Experiment. Technical Status Report.'' GSI, Darmstadt (2005) 406~p.

% Upgrade to progress report 2015
\bibitem{ProgressReport2014}
``CBM Progress Report 2014,'' GSI, Darmstadt (2015) 159 p.

% --------------------------------------------------------------------------------------

\bibitem{TDR_Magnet}
A.~Malakhov {\it et al.}, ``Technical Design Report for the CBM Superconducting Dipole Magnet,'' GSI, Darmstadt (2013) 80~p.

\bibitem{MVD_KOZIEL}
M.~Koziel, ``MVD Status: Integration,'' 25$^\mathrm{th}$ CBM Collaboration Meeting, Darmstadt, 20-24 April 2015.\\ 
\blueurl{https://indico.gsi.de/getFile.py/access?contribId=17&sessionId=9&resId=0&materialId=slides&confId=2960}

\bibitem{TDR_STS}
J.~Heuser {\it et al.}, ``Technical Design Report for the CBM Silicon Tracking System (STS),'' GSI, Darmstadt (2013) 167~p.

\bibitem{TDR_RICH}
C.~H\"{o}hne {\it et al.}, ``Technical Design Report for the CBM Ring Imagine Cherenkov (RICH),'' GSI, Darmstadt (2013) 201~p.

\bibitem{TDR_MUCH}
S.~Chattopadhyay {\it et al.}, ``Technical Design Report for the CBM Muon Chambers (MuCh),'' GSI, Darmstadt (2014) 192~p.

\bibitem{GEM}
%http://iopscience.iop.org/article/10.1088/1748-0221/8/12/C12002/meta
``Development of a GEM based detector for the CBM Muon Chamber (MUCH),''
S~Biswas et al 2013 JINST 8 C12002

\bibitem{TRD}
``TRD detector development for the CBM experiment,''
NIM A, Volume 732, 21 December 2013, Pages 375–379

\bibitem{TDR_TOF}
N.~Herrmann {\it et al.}, ``Technical Design Report for the CBM Time-of-Flight System (TOF),'' GSI, Darmstadt (2014) 182~p.

\bibitem{ECAL_KOROLKO}
I.~Korolko, ``CBM Calorimeter for SIS100 (TDR status),'' 25$^\mathrm{th}$ CBM Collaboration Meeting, Darmstadt, 20-24 April 2015.\\
\blueurl{https://indico.gsi.de/getFile.py/access?contribId=138&sessionId=29&resId=1&materialId=slides&confId=2960}

\bibitem{TDR_PSD}
F.~Guber {\it et al.}, ``Technical Design Report for the CBM Projectile spectator detector (PSD),'' GSI, Darmstadt (2014) 78~p.

% 1. MAPMT =============================================================================

\bibitem{H12700MANUAL}
\blueurl{https://www.hamamatsu.com/resources/pdf/etd/H12700_TPMH1348E.pdf}

\bibitem{CALVI}
``Characterization of the Hamamatsu H12700A-03 and R12699-03 multi-anode photomultiplier tubes,''
%http://dx.doi.org/10.1088/1748-0221/10/09/P09021
M. Calvi et al 2015 JINST 10 P09021 

\bibitem{CALVI2}
``Characterization of the Hamamatsu H12700A-03 multi-anode photomultiplier tube for the LHCb RICH upgrade,''
LHCb-INT-2015-006

\bibitem{H8500MANUAL}
\blueurl{https://www.hamamatsu.com/resources/pdf/etd/H8500_H10966_TPMH1327E.pdf}

\bibitem{MAPMTRADHARD}
T. Mahmoud RICH2016 proceedings

\bibitem{THECBMRICHPROJ16}
%Rad hardness here
NIM A, doi: 10.1016/j.nima.2016.05.102

\bibitem{THECBMRICHDET16}
%Rad hardness and WLS effect here
JINST 11 (2016) no.05, C05016

\bibitem{KOPFERDISS}
J.~Kopfer PhD thesis

% 2. READOUT ===========================================================================

\bibitem{TRBSITE}
Official TRB project web site,
\blueurl{http://trb.gsi.de/}

\bibitem{TRBDOCU}
TRB~v3 documentation,
\blueurl{http://jspc29.x-matter.uni-frankfurt.de/docu/trb3docu.pdf}

\bibitem{DPB}
Wojciech M. Zabołotny and Grzegorz Kasprowicz
``Data processing boards design for CBM experiment'',
Proc. SPIE 9290, Photonics Applications in Astronomy, Communications, Industry, and High-Energy Physics Experiments 2014, 929023 (November 25, 2014); doi:10.1117/12.2073377;

\bibitem{FLES}
``A First-level Event Selector for the CBM Experiment at FAIR,''
%http://iopscience.iop.org/article/10.1088/1742-6596/331/2/022006/meta
J de Cuveland et al 2011 J. Phys.: Conf. Ser. 331 022006

\bibitem{DABC}
``Data acquisition and online monitoring software for CBM test beams,''
%http://iopscience.iop.org/article/10.1088/1742-6596/396/1/012001/meta
J Adamczewski-Musch et al 2012 J. Phys.: Conf. Ser. 396 012001

% 3. SETUPS ============================================================================

\bibitem{BEAMTIME}
``Common CBM beam test of the RICH, TRD and TOF subsystems at the CERN PS T9 beam line in 2014,''
CBM Progress Report 2014, p.9

\bibitem{TRDBEAMTIME}
``Test of M\"unster CBM-TRD real-size detector and radiator prototypes at the CERN PS/T9 beam line,''
CBM Progress Report 2014, p.78

\bibitem{CERNPST9}
``Information about the T9 beam line and experimental facilities,''
\blueurl{http://home.web.cern.ch/sites/home.web.cern.ch/files/file/spotlight_students/information_about_the_t9_beam_line_and_experimental_facilities.pdf}

\bibitem{GASSYS}
``CBM RICH PROTOTYPE GAS SYSTEM,''
L.M. Kotchenda, P.A. Kravtsov

\bibitem{MIRRORMIS}
``Determination of tolerances of mirror displacement and radiator gas impurity for the CBM RICH detector,''
J.~Adamczewski-Musch et al,
doi:~10.1016/j.nima.2014.04.074

\bibitem{JORDANPR14}
``Mirror misalignment control system and prototype setup,''
CBM Progress Report 2014, p.56

\bibitem{LED}
Roithner UVTOP240 datasheet,
\blueurl{http://www.roithner-laser.com/datasheets/led_deepuv/uvtop240.pdf}

\bibitem{WLSINFLUENCE}
``Influence of wavelength-shifting films on multianode PMTs with UV-extended windows,''
NIM A, Volume 783, 21 May 2015, Pages 43–50

\bibitem{SYSCORE}
http://www.rz.uni-frankfurt.de/39888789/syscore

\bibitem{ALPHALAS}
Alphalas Picopower-LD series datasheet,
\blueurl{http://www.alphalas.com/images/stories/products/lasers/Picosecond_Pulse_Diode_Lasers_with_Driver_PICOPOWER-LD_ALPHALAS.pdf}

% 4. SOFT ==============================================================================

%Публикации о CbmRoot вшивые
\bibitem{CBMROOT}
%https://indico.cern.ch/event/408139/contributions/979676/attachments/815543/1117470/cbmroot_CHEP06.pdf
%https://www.researchgate.net/publication/242631488_CbmRoot_Simulation_and_Analysis_framework_for_CBM_Experiment
%http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.117.5935&rep=rep1&type=pdf

\bibitem{FLESnet}
FLESnet development repository,
\blueurl{https://github.com/cbm-fles/flesnet}

\bibitem{HLD}
%https://repository.gsi.de/record/52192/files/PHN-SIS18-ACC-41.pdf
``HADES trbnet data formats for DABC and Go4,''
PHN-SIS18-ACC-41
GSI SCIENTIFIC REPORT 2012, p.297

\bibitem{TDLCALIB}
R. Szplet, J. Kalisz, and R. Pelka. Nonlinearity correction of the integrated time-to-digital converter with direct coding. IEEE Transactions on Instrumentation and Measurement, 46:449–453, April 1997.

\bibitem{RECOPEPAN}
Письма в ЭЧАЯ. 2009. Т.6, №2(151). С.260-284
%``Быстрые алгоритмы распознавания колец и идентификации электронов в детекторе RICH эксперимента CBM''
%Лебедев, Ососков, письма в ЭЧАЯ, 2009

\bibitem{RECO2}
``Fast Parallel Ring Recognition Algorithm in the RICH Detector of the CBM Experiment at FAIR,''
ACAT2010 proceedings
%13th International Workshop on Advanced Computing and Analysis Techniques in Physics Research
%February 22-27, 2010
%Jaipur, India

% 5. RESULTS ===========================================================================

\bibitem{PEPAN}
J.~Adamczewski-Musch et al,
``Tests of the CBM RICH readout and DAQ prototype'',
PEPAN letters

\bibitem{DUERR}
M.~D\"urr, private communication

\bibitem{SPC}
D.V. O’Connor, D. Phillips, Time Correlated Single Photon Counting, Academic Press, London 1984

\bibitem{ToTinNoise}
Time over threshold in the presence of noise.

% ======================================================================================

\end{thebibliography}
