\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Список литературы}

% Intro --------------------------------------------------------------------------------------------

\bibitem{CBMBook}
\textit{B.~Friman, C.~H\"{o}hne, J.~Knoll, S.~Leupold, J.~Randrup, R.~Rapp and P.~Senger} //
The CBM physics book: Compressed baryonic matter in laboratory experiments,
Lect.\ Notes Phys.\ {\bf 814} (2011) pp. 980.

\bibitem{Chen}
Courtesy of Paul Sorensen and Chun Shen \\
\blueurl{http://u.osu.edu/vishnu/}

\bibitem{THERMUS}
\textit{S. Wheaton, J. Cleymans, M. Hauer} //
THERMUS --- A Thermal Model Package for ROOT,
Computer Physics Communications, Volume~180, Issue~1, January~2009, Pages 84--106
% http://www.sciencedirect.com/science/article/pii/S0010465508002750
% https://arxiv.org/pdf/hep-ph/0407174.pdf

\bibitem{CBMSIS100}
%\textit{P.~Senger and V.~Friese} //
%The CBM Collaboration: Nuclear Matter Physics at SIS-100,
%GSI, Darmstadt (2012) 18~p.

\bibitem{CBM_TSR}
Compressed Baryonic Matter Experiment. Technical Status Report.
GSI, Darmstadt (2005) 406~p.

% Upgrade to progress report 2015
\bibitem{ProgressReport2014}
\textit{V.~Friese and C.~Sturm} // % editors
CBM Progress Report 2014,
ISBN: 978-3-9815227-2-3, 2015.
%GSI, Darmstadt (2015) 159 p.

% Chapter 1 ----------------------------------------------------------------------------------------

\bibitem{FAIR}
\textit{H. H. Gutbrod} // % Editor in Chief
FAIR Baseline Technical Report,
ISBN: 3-9811298-0-6, 2006.
%GSI, Darmstadt (2006) 92~p.
%\blueurl{www.fair-center.eu/fileadmin/fair/publications_FAIR/FAIR_BTR_1.pdf}

%\bibitem{Randrup}
%\textit{J. Randrup and J. Cleymans} //
%Maximum freeze-out baryon density in nuclear collisions,
%Phys. Rev. C 74, 047901

% Optimal conditions for exploring high-density baryonic matter --- ?
% Exploring high-density baryonic matter: Maximum freeze-out density --- ?

\bibitem{NUSTAR}
\blueurl{http://www.fair-center.eu/for-users/experiments/nustar.html}

\bibitem{PANDA}
\blueurl{https://panda.gsi.de/}

\bibitem{APPA}
\blueurl{http://www.fair-center.eu/for-users/experiments/appa.html}

\bibitem{TDR_Magnet}
\textit{A.~Malakhov and A.~Shabunov} // % editors
Technical Design Report for the CBM Superconducting Dipole Magnet,
GSI, Darmstadt (2013) 80~p.

\bibitem{MVD_KOZIEL}
\textit{M.~Koziel} //
MVD Status: Integration,
25$^\mathrm{th}$ CBM Collaboration Meeting, Darmstadt, 20-24 April 2015.
\blueurl{https://indico.gsi.de/getFile.py/access?contribId=17&sessionId=9&resId=0&materialId=slides&confId=2960}

\bibitem{TDR_STS}
\textit{J.~Heuser et~al.} //
Technical Design Report for the CBM Silicon Tracking System (STS),
 GSI, Darmstadt (2013) 167~p.

\bibitem{TDR_RICH}
\textit{C.~H\"{o}hne et~al.} //
Technical Design Report for the CBM Ring Imagine Cherenkov (RICH),
GSI, Darmstadt (2013) 201~p.

\bibitem{TDR_MUCH}
\textit{S.~Chattopadhyay et~al.} //
Technical Design Report for the CBM Muon Chambers (MuCh),
GSI, Darmstadt (2014) 192~p.

\bibitem{GEM}
\textit{S.~Biswas et~al.} //
Development of a GEM based detector for the CBM Muon Chamber (MUCH),
2013 JINST 8 C12002.
%http://iopscience.iop.org/article/10.1088/1748-0221/8/12/C12002/meta

\bibitem{TRD}
\textit{M.~Petris et~al.} //
TRD detector development for the CBM experiment,
NIM A, Volume~732, 21~December~2013, pp.~375--379.

\bibitem{TDR_TOF}
\textit{N.~Herrmann et~al.} //
Technical Design Report for the CBM Time-of-Flight System (TOF),
GSI, Darmstadt (2014) 182~p.

\bibitem{ECAL_KOROLKO}
\textit{I.~Korolko} //
CBM Calorimeter for SIS100 (TDR status),
25$^\mathrm{th}$ CBM Collaboration Meeting, Darmstadt, 20-24 April 2015.\\
\blueurl{https://indico.gsi.de/getFile.py/access?contribId=138&sessionId=29&resId=1&materialId=slides&confId=2960}

\bibitem{TDR_PSD}
\textit{F.~Guber et~al.} //
Technical Design Report for the CBM Projectile spectator detector (PSD),
GSI, Darmstadt (2014) 78~p.

\bibitem{SPADIC}
\blueurl{http://spadic.uni-hd.de/} \\
\blueurl{http://spadic.uni-hd.de/publications/}

\bibitem{PADI}
\blueurl{http://ieeexplore.ieee.org/document/4774801/}

\bibitem{DPB}
\textit{W.~M.~Zabołotny and G.~Kasprowicz} //
Data processing boards design for CBM experiment,
Proc. SPIE 9290, Photonics Applications in Astronomy, Communications, Industry, and High-Energy Physics Experiments 2014, 929023 (November 25, 2014); doi:10.1117/12.2073377;

\bibitem{FLES}
\textit{J~de~Cuveland et~al.} //
A First-level Event Selector for the CBM Experiment at FAIR,
2011 J. Phys.: Conf. Ser. 331 022006.
%http://iopscience.iop.org/article/10.1088/1742-6596/331/2/022006/meta

\bibitem{AkishinaCA}
\textit{V. Akishina and I. Kisel} //
Time-based Cellular Automaton track finder for the CBM experiment,
2015 J. Phys.: Conf. Ser. 599 012024

\bibitem{KALMAN}
\todo

\bibitem{RichHistory}
\textit{J. Engelfried} //
Cherenkov Light Imaging --- Fundamentals and recent Developments,
% https://arxiv.org/pdf/1009.0052.pdf

% см. http://localhost/Lib/Long_term_experience_and_performance_of_COMPASS_RI.pdf
\bibitem{CMAD}
\textit{M.Chiosso et al.} //
A full custom front-end ASIC Prototype “CMAD” for COMPASS-RICH-1 particle detector system,
IEEE Nucl. Sci. Symp. Conf. Rec. 2008 (2008) 1495

\bibitem{CLAM}
\textit{S.Costa, S.Dalla Torre, D.Faso, J-Ch.Gayde, A.Latina, F.Tessarotto} //
CLAM, a continuous line alignment and monitoring method for RICH mirrors,
NIM A, Volume~553, 11~November~2005, Issues~1--2, pp.~135--139

\bibitem{KOPFERDISS}
J.~Kopfer PhD thesis, Bergische Universit\"{a}t Wuppertal.

\bibitem{RICHreco}
\todo

\bibitem{URQMD}
\todo

% Chapter 2 ----------------------------------------------------------------------------------------

\bibitem{Golovanov}
\textit{Голованов Н.Н.} //
Геометрическое моделирование,
2002 Физматлит ISBN 5-94052-048-0

\bibitem{NETGEN}
\blueurl{https://ngsolve.org/}

\bibitem{NURBS}
\blueurl{https://en.wikipedia.org/wiki/Non-uniform_rational_B-spline}

\bibitem{AIDA}
\blueurl{http://aidasoft.web.cern.ch/}

\bibitem{USOLIDS}
\blueurl{http://aidasoft.web.cern.ch/USolids}

\bibitem{GDML}
\blueurl{https://gdml.web.cern.ch/GDML/}

\bibitem{FASTRAD}
\blueurl{http://www.fastrad.net/}

\bibitem{SimpleGeo}
\textit{C. Theis et al} //
SimpleGeo --- New Developments in the Interactive Creation and Debugging of Geometries for Monte Carlo Simulations,
Progress in NUCLEAR SCIENCE and TECHNOLOGY, Vol. 2, pp.587-590 (2011)

\bibitem{Cinzia}
\textit{C. Luzzi and F. Carminati} //
TGeoCad: an Interface between ROOT and CAD Systems,
2014 J. Phys.: Conf. Ser. 523 012017
% http://iopscience.iop.org/article/10.1088/1742-6596/523/1/012017/pdf

\bibitem{OCCtech}
\blueurl{https://www.opencascade.com/content/core-technology}

\bibitem{Tobias}
\textit{T. Stockmanns} //
STEP-to-ROOT --- from CAD to Monte Carlo Simulation,
2012 J. Phys.: Conf. Ser. 396 022050
% http://iopscience.iop.org/article/10.1088/1742-6596/396/2/022050/pdf

\bibitem{RichCameraInField}
\textit{C. Welzbacher, T. Mahmoud, C. Pauly, and C. Hohne} //
RICH design with tilted mirrors,
CBM progress report 2012

% Chapter 3 ----------------------------------------------------------------------------------------

\bibitem{H12700MANUAL}
Hamamatsu H12700 manual,
\blueurl{https://www.hamamatsu.com/resources/pdf/etd/H12700_TPMH1348E.pdf}

\bibitem{CALVI}
\textit{M. Calvi et~al.} //
Characterization of the Hamamatsu H12700A-03 and R12699-03 multi-anode photomultiplier tubes,
2015 JINST 10 P09021.
%Marta Calvi, Paolo Carniti, Lorenzo Cassina, Claudio Gotti, Matteo Maino, Clara Matteuzzi, Gianluigi Pessina
%http://dx.doi.org/10.1088/1748-0221/10/09/P09021

\bibitem{CALVI2}
\textit{M. Calvi et~al.} //
Characterization of the Hamamatsu H12700A-03 multi-anode photomultiplier tube for the LHCb RICH upgrade,
LHCb-INT-2015-006.
%M. Calvi, P. Carniti, L. Cassina, C. Gotti, M. Maino, C. Matteuzzi and G. Pessina

%http://pessina.mib.infn.it/Biblio/Biblio_Articoli/LHCb-INT-2015-006.pdf

\bibitem{H8500MANUAL}
\blueurl{https://www.hamamatsu.com/resources/pdf/etd/H8500_H10966_TPMH1327E.pdf}

\bibitem{MCdynodeSys}
Photomultiplier tubes, Basics and Applications, Hamamatsu Photonics K.K.
%http://www.hamamatsu.com/resources/pdf/etd/PMT_handbook_v3aE.pdf

\bibitem{MAPMTRADHARD}
T. Mahmoud RICH2016 proceedings.

\bibitem{THECBMRICHPROJ16}
%Rad hardness here
\textit{C.~Pauly et~al.} //
The CBM RICH project,
NIM A 2016,
doi: 10.1016/j.nima.2016.05.102.

\bibitem{THECBMRICHDET16}
%Rad hardness and WLS effect here
\textit{S.~Reinecke et~al.} //
The CBM-RICH detector,
JINST 11 (2016) no.05, C05016.

\bibitem{TRBSITE}
Official TRB project web site,
\blueurl{http://trb.gsi.de/}

\bibitem{CAHIT}
\textit{C.~Ugur, S.~Linev, J.~Michel, T.~Schweitzer, and M.~Traxler} //
A novel approach for pulse width measurements with a high precision (8 ps RMS) TDC in an FPGA,
2016 JINST 11 C01046.
% Topical Workshop on Electronics for Particle Physics 2015,
% September 28 th – October 2 nd , 2015
% Lisbon, Portugal

% либо более старая
% ``264 Channel TDC Platform Applying 65 Channel High Precision (7.2 ps RMS) FPGA Based TDCs,''
% 978-1-4799-1186-8/13/$31.00 ©2013 IEEE

\bibitem{TRBDOCU}
TRB~v3 documentation,
\blueurl{http://jspc29.x-matter.uni-frankfurt.de/docu/trb3docu.pdf}

\bibitem{DIRICH}
\textit{J.~Michel, M.~Faul, J.~Friese, C.~H\"{o}hne, K.-H.~Kampert, V.~Patel, C.~Pauly, D.~Pfeifer, P.~Skott, M.~Traxler, and C.~Ugur} //
Electronics for the RICH detectors of the HADES and CBM experiments,
2017 JINST 12 C01072.
%Topical Workshop on Electronics for Particle Physics,
%26–30 September 2016,
%Karlsruhe Institute of Technology (KIT), Karlsruhe, Germany

\bibitem{DABC}
\textit{J.~Adamczewski-Musch et~al.} //
Data acquisition and online monitoring software for CBM test beams,
%http://iopscience.iop.org/article/10.1088/1742-6596/396/1/012001/meta
2012 J. Phys.: Conf. Ser. 396 012001.

\bibitem{BEAMTIME}
\textit{C.~Bergmann et~al.} //
Common CBM beam test of the RICH, TRD and TOF subsystems at the CERN PS T9 beam line in 2014,
CBM Progress Report 2014, p.9.

\bibitem{TRDBEAMTIME}
\textit{C.~Bergmann et~al.} //
Test of M\"unster CBM-TRD real-size detector and radiator prototypes at the CERN PS/T9 beam line,
CBM Progress Report 2014, p.78.
% C. Bergmann, D. Emschermann, R. Berendes, N. Heine, M. Kohn, W. Verhoeven, and J. P. Wessels

\bibitem{TOFBEAMTIME}
\textit{M.~Petris, D.~Batros, G.~Caragheorghropol et~al.} //
Prototype with the basic architecture for the CBM-TOF inner wall tested in close to real conditions,
2016 J. Phys.: Conf. Ser. 724 012037.
% M.~Petris, D.~Batros, G.~Caragheorgheopol, F.~Constantin, M.~Petrovici, L.~Radulescu, V.~Simion, I.~Deppner, N.~Herrmann, C.~Simon

\bibitem{CERNPST9}
Information about the T9 beam line and experimental facilities,
\blueurl{http://home.web.cern.ch/sites/home.web.cern.ch/files/file/spotlight_students/information_about_the_t9_beam_line_and_experimental_facilities.pdf}

\bibitem{GASSYS}
\textit{L.M. Kotchenda, P.A. Kravtsov} //
CBM RICH PROTOTYPE GAS SYSTEM.

\bibitem{MIRRORMIS}
\textit{J.~Adamczewski-Musch et~al.} //
Determination of tolerances of mirror displacement and radiator gas impurity for the CBM RICH detector,
doi:~10.1016/j.nima.2014.04.074

\bibitem{JORDANPR14}
\textit{J.~Bendarouach, C.~H\"{o}hne, and T.~Mahmoud} //
Mirror misalignment control system and prototype setup,
CBM Progress Report 2014, p.56.

\bibitem{LED}
Roithner UVTOP240 datasheet,
\blueurl{http://www.roithner-laser.com/datasheets/led_deepuv/uvtop240.pdf}

\bibitem{WLSINFLUENCE}
\textit{M. D\"{u}rr, J. Kopfer et~al.} //
Influence of wavelength-shifting films on multianode PMTs with UV-extended windows,
NIM A, Volume 783, 21 May 2015, Pages 43–50.

\bibitem{ALPHALAS}
Alphalas Picopower-LD series datasheet,
\blueurl{http://www.alphalas.com/images/stories/products/lasers/Picosecond_Pulse_Diode_Lasers_with_Driver_PICOPOWER-LD_ALPHALAS.pdf}

\bibitem{SYSCORE}
\blueurl{http://www.rz.uni-frankfurt.de/39888789/syscore}

\bibitem{NXYTER}
\textit{A.S.~Brogna et~al.} //
The n-XYTER Reference Manual,
\blueurl{https://cbm-wiki.gsi.de/foswiki/pub/Public/PublicNxyter/nXYTER.pdf}

%Публикации о CbmRoot вшивые
\bibitem{CBMROOT}
\blueurl{http://cbmroot.gsi.de/}
%https://indico.cern.ch/event/408139/contributions/979676/attachments/815543/1117470/cbmroot_CHEP06.pdf
%https://www.researchgate.net/publication/242631488_CbmRoot_Simulation_and_Analysis_framework_for_CBM_Experiment
%http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.117.5935&rep=rep1&type=pdf

\bibitem{FLESnet}
FLESnet development repository,
\blueurl{https://github.com/cbm-fles/flesnet}

\bibitem{HLD}
\textit{J.~Adamczewski-Musch, S.~Linev, E.~Ovcharenko, and C.~Ugur} //
HADES trbnet data formats for DABC and Go4,
PHN-SIS18-ACC-41, GSI SCIENTIFIC REPORT 2012, p.297.
%https://repository.gsi.de/record/52192/files/PHN-SIS18-ACC-41.pdf

\bibitem{TDLCALIB}
\textit{R.~Szplet, J.~Kalisz, and R.~Pelka} //
Nonlinearity correction of the integrated time-to-digital converter with direct coding,
IEEE Transactions on Instrumentation and Measurement, 46:449–453, April 1997.

\bibitem{RECOPEPAN}
\textit{С.А.~Лебедев, Г.А.~Ососков} //
Быстрые алгоритмы распознавания колец и идентификации электронов в детекторе RICH эксперимента CBM,
Письма в ЭЧАЯ. 2009. Т.6, №2(151). С.260-284.

\bibitem{RECO2}
\textit{S.~Lebedev, C.~H\"{o}hne, I.~Kisel, G.~Ososkov} //
Fast Parallel Ring Recognition Algorithm in the RICH Detector of the CBM Experiment at FAIR,
ACAT2010 proceedings.
%13th International Workshop on Advanced Computing and Analysis Techniques in Physics Research
%February 22-27, 2010
%Jaipur, India

\bibitem{PEPAN}
\textit{E.~Ovcharenko, S.~Belogurov et~al.} //
Tests of the CBM RICH readout and DAQ prototype,
PEPAN letters.

\bibitem{DUERR}
M.~D\"urr, private communication.

\bibitem{SPC}
\textit{D.V. O’Connor, D. Phillips} //
Time Correlated Single Photon Counting, Academic Press, London 1984.

\bibitem{ToTinNoise}
\textit{F.~Gonnella, V.~Kozhuharov, M.~Raggi} //
Time over threshold in the presence of noise,
NIM A, Volume 791, p. 16-21.
% https://arxiv.org/pdf/1412.1743.pdf
% http://www.sciencedirect.com/science/article/pii/S0168900215005161

\end{thebibliography}

%http://iopscience.iop.org/article/10.1088/1748-0221/11/01/C01046/meta
%http://iopscience.iop.org/article/10.1088/1748-0221/12/01/C01072/meta
